### 2012-04-18 1.1.2.tex
More arranging.
chapters 2 and 4 have been swapped

% 1.1.2: Early generativism

@@

>>>>

\subsection{Early generativism}

@@

\citeauthor{Anderson1974} sees the duplication of \textsc{Backness Harmony} as both sequence structure constraint and phonological rule as a foregone conclusion
.The tendency of sequence structure constraints to duplicate phonological rules was noted by \citet[][401f.]{Stanley1967} and in \emph{SPE} (p.~382) in the discussion of morpheme structure constraints, and is labeled ``the duplication problem'' by \citet[][?]{Kenstowicz1977}.

### 2012-04-18 2.1.1.tex
More arranging.
chapters 2 and 4 have been swapped

% 2.1.1: Data sources

The English CELEX database \citep{CELEX},

\citet{Aronoff1976}

\citet{Harley2009}

\citet{Taft1975} ?
\citet{Taft1981} ?
\citet{Taft2004a} ?

\citet{Halle1962}

>>>>

\subsection{Gradience in judgements}

at least as far back as \emph{LSLT} \citep{LSLT}

%and has become a recent feature of the discussion
is that non-gradient models are totally incompatible with psycholinguistic results.

\subsubsection{Task model}

\citet[][16]{Schutze1996}

\citet{Schutze2005}
\citet{Schutze2011}

\citet{Coleman1997}

\subsubsection{Falsifiability}

\citet{Armstrong1983}

% wordlikeness critique
\citet{Yang2008a}

a mix of ``declarative'' knowledge,
corresponding to rote facts and thus the lexicon,
and ``procedural'' knowledge, or knowledge of generative procedures 
(in the sense of J. \citealt{Anderson1993}).

% math cog
\citet{Logan1988}
\citet{Sfard1991}
\citet{Delazer2005}

### 2012-04-18 2.1.2.tex
More arranging.
chapters 2 and 4 have been swapped

% 2.1.2: Syllabification

It is necessary to split medial consonant clusters into the codas and onsets that make them up. While CELEX provides syllabified transcriptions, no description of the syllabification procedure is given in the documentation, and inspection of these syllabifications suggests the procedure used is not fully systematic. For instance, \emph{chemistry} is syllabified as [ˈkɛ.mɪ.strɪ] but \emph{ministry} as [ˈmɪ.nɪs.trɪ].\footnote{Note that word-final \emph{y} is generally lax [ɪ] in RP \citep[][294]{AOE2}.}
This putative [ɪ.strɪ $\sim$ ɪs.trɪ] contrast, and many other such contrasts in the CELEX data, are dubious simply because there is no clear evidence that contrastive syllabification occurs in any language. Apparent counterexamples appear to be effects of vowel or consonant length \citep[e.g.,][]{Elfner2006}, word stress, or morphological structure, none of which contrast \emph{chemistry} and \emph{ministry}.

An automated syllabification system was constructed and applied to medial clusters in the CELEX data. This system need only deal with simplex English words that contain the medial consonant clusters which are the focus of this study.  There is, for instance, no need to address the status of ``ambisyllabic'' consonants, i.e., singleton medial consonants preceded by a stressed lax vowel \citep[][219f.]{Rubach1996}, or to address morphological effects on syllabification. The technique used is a variation on the theme of onset maximization \citep[42f.]{Kahn1976}, which parses word-medial clusters so that the onset is as large as possible. Medial clusters in words like \emph{neu}[.tr]\emph{on} or \emph{bi}[.str]\emph{o} are found in word-initial position (e.g., [tr]\emph{ansit}, [str]\emph{ike}), and onset maximization leaves the coda of the first syllable empty. However, in words like \emph{mi}[n.str]\emph{el}, the [nstr] cluster does not occur word-initially; here the maximal onset is [str], and the [n] is assigned to the coda.

There is one case where unchecked maximization of medial onsets produces incorrect syllabifications. When a medial consonant cluster is preceded by a stressed lax vowel, as in words like \emph{propaga}[n.d]\emph{a}, \emph{whi}[s.p]\emph{er}, \emph{vi}[s.t]\emph{a}, or \emph{bi}[s.k]\emph{uit}, the first consonant of the cluster checks the lax vowel \citep[e.g.,][3]{Hammond1997}. Onset maximization makes the right predictions for words like \emph{propaganda}, where the medial cluster cannot be an onset, but \citet[][55]{Harris1994} notes that it makes the wrong predictions when the medial cluster is a valid onset: in \emph{whisper}, \emph{vista}, and \emph{biscuit}, it incorrectly assigns [sp, st, sk] to the medial onset, leaving the coda empty. The approach adopted here is to first apply onset maximization, then to reassign the first consonant of a medial onset to the preceding coda if it is immediately preceded by a stressed lax vowel.

If the English affricates [tʃ, dʒ] are treated as sequences and not individual segments, this addition to the standard onset maximization technique would itself make the wrong prediction for medial affricates preceded by lax stressed vowels in words like \emph{ra}[.tʃ]\emph{et} or \emph{a}[.dʒ]\emph{ile}, incorrectly assigning the stop and fricative portions to separate syllables. For this reason, it is assumed here that affricates are single segments for the purposes of syllabification. This assumption is motivated by the fact that affricates pattern with simple segments in many languages; for instance, the only word-initial consonant clusters in Classical Nahua are affricates [ts, tʃ, tɬ] \citep[][9]{Launey2011}.

%In fact, [t.ʃ, d.ʒ] clusters are not found in simplex English words, despite the fact that that affricates occur as medial onsets in clusters (e.g., \emph{tru}[n.tʃ]\emph{eon}, \emph{so}[l.dʒ]\emph{er}).

>>>>

\subsection{The ontology of wordlikeness}

\subsubsection{Gross phonotactic violation}

position in \citet{SPE}

\citet{Shibatani1973}
\citet{Hooper1973}

peripheral \citep[in the sense of][81]{LGB}

As an example of this applied ot phonotactics, 
\citet{Borowsky1989} assumes that there are peripheral morph-internal syllable contact clusters.

\subsubsection{Phonological statistics}

\citet{SPE}

This statement is made very strongly by \citet{Coleman1997}

\subsubsection{Lexical similarity}

\citet{LSLT}

\citet{Greenberg1964}
\citet{Ohala1986b}

A recent, very articulated model is presented by \citet{Bailey2001}.

% simple model
This is simply because more complex models fail to

% similarity vs. rules
% as a final note, \citet{Hahn1998}
